Resilience and Home-Space for WSTS

### 2024-01-03 diapo/presentation.tex
up

 \column{0.65\textwidth}
\phantom{Fridge.png} \\
{\sf Bad} state is when temperature is too high \\
 {\sf Good} state is temperature low enough \\

@@

@@

  \end{frame}
%vvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvv
  \begin{frame}{... on effectivity}

@@

@@

      {\tiny
\bibliography{bibliography}
}

>>>>

 \column{0.65\textwidth}
\phantom{Fridge.png} \\
\phantom{Fridge.png} \\
{\sf Bad} state = temperature is too high \newline

 {\sf Good} state = temperature low enough \\

@@

   \begin{center}
 	\begin{figure}
 	% \hspace{-2.cm}
\includegraphics[width=.25\textwidth]{WSTS_def}
	\end{figure}
\end{center}

@@

  \end{frame}
%vvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvv
  \begin{frame}{WSTS with strong compatibility}

\begin{definition}
A  Well-Structured Transition System {\em with \textcolor{red}{strong} compatibility}  $\mathscr{S}=(S, \rightarrow, \leq)$
is a transition system $(S, \rightarrow)$
equipped with a wqo ${\leq} \subseteq S \times S$ such that   
the transition relation $ \rightarrow$ is \textcolor{red}{strongly} (upward) compatible with $\leq$, i.e., for all 
$s_1, t_1 , s_2 \in S$
	with $s_1 \leq s_2$  and $s_1 \rightarrow t_1$, there exists 
	$t_2 \in S$ with 
	$t_1 \leq t_2$ and $s_2 \textcolor{red}{\rightarrow} t_2$.
\end{definition}

\begin{center}
 	\begin{figure}
 	% \hspace{-2.cm}
\includegraphics[width=.25\textwidth]{WSTS_strong}
	\end{figure}
\end{center}

\phantom{fridge}\\
\phantom{ undecidable for WSTS} \\
\phantom{ undecidable for WSTS} \\

  \end{frame}
%vvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvv
  \begin{frame}{On effectivity}

Ideal =
\begin{itemize}
 \item downward-closed % is any set $D \subseteq X$ such that if $y \leq x$ and $x \in D$ then $y \in D $. 
 \item directed % i.e. it is nonempty and for every $a,b \in D$, there exists $c \in D$ such that $a \leq c$ and $b \leq c$.
\end{itemize}

  \todo[inline,color=blue!20]{ 
Définir Ideals and ideals.
}

\hspace{-2cm}

 effective = 
 \begin{itemize}
\item s $\to$ t decidable 
\item membership decidable 
\item $\leq$ decidable 
\item membership in $Ideals(S)$ decidable 
\item inclusion of ideals decidable
\end{itemize}

  \end{frame}
%vvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvv
  \begin{frame}{On effectivity}

@@

Définir rapidement les VASS

 \begin{definition} 
A {\em vector addition system with (control-)states (VASS)} in dimension $d$ ($d$-VASS for short) is a finite $\mathds{Z}^d$-labeled directed graph $V = (Q,T)$, where $Q$ is the set of {\em control-states}, and $T \subseteq Q \times \mathds{Z}^d \times Q$ is the set of {\em control-transitions}. 
 \end{definition}

@@

      {\tiny
\bibliography{bib}
}
